%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer | MES (Manufacturing Execution System) Engineer} % Job title
    {Opex Consulting Group} % Organization
    {Indonesia - Singapore - Malaysia} % Location
    {Apr. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement and Deliver Solution for Digital Transformation in Manufacturing 4.0}
        \item {Configured System Administration of Windows Server 2019}
        \item {Integration of Enterprise Software}
        \item {Administration of SQL Database Server}
        \item {Setup Observability Tools}
        \item {Opcenter Siemens Execution Core / Electronics (Modelling Bussiness Process of Physical, Process, Execution) MES}
        \item {Opcenter Siemens Execution Core / Electronics (Configuring Bussiness Logic in Designer, and manage Portal Studio) MES}
        \item {Design and Create Custom Application for Manufacturing Process using (.NET and Mendix Siemens)}
        \item {Manage Google Cloud Platform}
        \item {Knowledge gained: Software Enterprise, Process Control, Aquisition Data, Production Management, Quality, Material Management, Maintenance Management, Data Integration}
        \item {Tech Stack: C\#, Google Cloud Platform, Opcenter MES Siemens software, Desktop Application .NET, Siemens Mendix, System Administration Windows Server 2019, NLB (Network Load Balancer), IIS 8, Redis, Windows Service .NET, ASP.NET, Prometheus, AlertManager, Grafana, Grafana Loki, Promtail}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {Vechr Community} % Organization
    {Indonesia} % Location
    {Jan. 2022 - Jan 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing an application IIoT refer to ISA-95}
        \item {Developing an Event driven Application Monitoring Machine using Nest/Typescript and Vue/Typescript}
        \item {Create Realtime Historian data machine using Web Socket}
        \item {Create Audit History app}
        \item {Create Drag \& Drop Chart (Widget) for Dashboard, and connect with Web socket to achieve Realtime Chart System}
        \item {Manage Database Postgresql and Time Series Database (InfluxDB)}
        \item {Create Deployment Kubernetes using Helm Chart}
        \item {Sending Alert to SMTP}
        \item {Knowledge gained: Event Driven Architecture, Microservices Pattern, Usage of Message Broker (NATS, MQTT), Container Orchestration, Manufacturing System, Design Authentication and Authorization, Restfull Pagination}
        \item {Tech Stack: Kubernetes \& Helm Chart, Terraform, Terragrunt, GCP, Docker, NATS (Messaging System and Caching), MQTT, GIT Hooks, NGINX API Gateway, Node Mailer, Nest, Prisma ORM, State Management(pinia), Vue/Typescript, Husky, Commitizen, linter}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer (Freelance)} % Job title
    {ThreeSixty} % Organization
    {Remote} % Location
    {Feb. 2022 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created Frontend Application.}
        \item {Doing Integration with Backend Rest API.}
        \item {Collaborative using Agile (JIRA).}
        \item {Knowledge gained: Vuejs/Typescript, Docker, JWT auth, Stripe}
      \end{cvitems}
    }
  

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {Synergy Engineering} % Organization
    {BSD Tangerang, Indonesia} % Location
    {Jan. 2021 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Application SBS (Synergy Bussines Suite) to create Front End and Backend using Ruby On Rails Framework.}
        \item {Collaborate team with Kanban Methodologies using Trello.}
        \item {Create API backend Rails with Postgresql.}
        \item {Create Drawing tagging for Engineering Drawing.}
        \item {Version Control System using Git and Gitlab.}
        \item {Knowledge gained: Database Design, Authentication \& Authorization, GIT FLOW}
        \item {Tech Stack: ruby, rails MVC, Javascript, HTML (.erb)/ Slim, SASS, NPM, GITLAB, Leafletjs, Cancancan, Devise, Dropzonejs, Bootstrap 4.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {L'Oréal (PT Yasulor Indonesia)} % Organization
    {North Cikarang, West Java, Indonesia} % Location
    {Sept. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Doing Software Development “Inspection Check application using ASP.NET and VB.NET”.}
        \item {Doing Maintenance \& Preventive on Filling Machine.}
        \item {Doing Maintenance \& Preventive Process Machine SKID.}
        \item {Knowledge Gained: VB.net, ASP.net, Desktop Application, Maintenance system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {PT Datareka Integrasia Teknologi}
    {Cimahi, West Java, Indonesia} % Location
    {March. 2017 - July. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Troubleshooting Board PCB of Security Panel}
        \item {Assembly Board PCB Controller and Power Supply using SMD Component}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Field Service Engineer} % Job title
    {Midea Electronics Indonesia} % Organization
    {North Jakarta, Indonesia} % Location
    {Jun. 2016 - August. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance and repair Air Conditioner.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
