%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {kre Tech Community} % Organization
    {Indonesia} % Location
    {Jan. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing an application IIoT refer to ISA-95}
        \item {Developing an Event driven Application Monitoring Machine using Nest/Typescript and Vue/Typescript}
        \item {Create Realtime Historian data machine using Web Socket}
        \item {Create Drag \& Drop Chart (Widget) for Dashboard, and connect with Web socket to achieve Realtime Chart System}
        \item {Manage Database Postgresql and Time Series Database (InfluxDB)}
        \item {Create Deployment Kubernetes using Helm Chart}
        \item {Sending Alert to SMTP}
        \item {Knowledge gained: Event Driven Architecture, Microservices Pattern, Usage of Message Broker (NATS, MQTT), Container Orchestration, Manufacturing System, Design Authentication and Authorization, Restfull Pagination}
        \item {Tech Stack: Kubernetes \& Helm Chart, Docker, NATS, MQTT, GIT Hooks, Kong API Gateway, Node Mailer, Nest, Prisma, Pinia, Vue, Husky, Commitizen, linter}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Solutions Engineer} % Job title
    {Opex Consulting Group} % Organization
    {Indonesia - Singapore (hybrid)} % Location
    {Apr. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing an Application using Mendix Platform.}
        \item {Collaborate team using agile methodologies in Mendix Platform.}
        \item {Installing and Configuring MES (Manufacturing Execution System) Siemens Opcenter Core architecture, SMTP, Windows Server 2019, SQL Setup, Windows Failover, Microsoft NLB (Including SSL), SQL Server Always On, IIS 8}
        \item {Developing a Windows Service for Integration MES Siemens to another system like an ERP System and Machine/Scada Level using .NET Framework (v4.7.2, C\#)}
        \item {Manage Database SQL Server.}
        \item {Created Modelling MES Siemens based on Bussines Requirement. for Tracebility, Process Control, Aquisition Data, Production Management, Quality, Material Management.}
        \item {Design and Create Application for Manufacturing Process.}
        \item {Knowledge gained: Software Enterprise, Process Control, Aquisition Data, Production Management, Quality, Material Management, Maintenance Management, Data Integration}
        \item {Tech Stack: C\#, MES Siemens software, Desktop Application, Mendix, Windows Server 2019, Redis, Windows Service, ASP.NET}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer (Freelance)} % Job title
    {ThreeSixty} % Organization
    {Remote} % Location
    {Feb. 2022 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created Frontend Application.}
        \item {Doing Integration with Backend Rest API.}
        \item {Collaborative using Agile (JIRA).}
        \item {Knowledge gained: Vuejs/Typescript, Docker, JWT auth, Stripe}
      \end{cvitems}
    }
  

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {Synergy Engineering} % Organization
    {BSD Tangerang, Indonesia} % Location
    {Jan. 2021 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Application SBS (Synergy Bussines Suite) to create Front End and Backend using Ruby On Rails Framework.}
        \item {Collaborate team with Kanban Methodologies using Trello.}
        \item {Create API backend Rails with Postgresql.}
        \item {Create Drawing tagging for Engineering Drawing.}
        \item {Version Control System using Git and Gitlab.}
        \item {Knowledge gained: Database Design, Authentication \& Authorization, GIT FLOW}
        \item {Tech Stack: ruby, rails MVC, Javascript, HTML (.erb)/ Slim, SASS, NPM, GITLAB, Leafletjs, Cancancan, Devise, Dropzonejs, Bootstrap 4.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {L'Oréal (PT Yasulor Indonesia)} % Organization
    {North Cikarang, West Java, Indonesia} % Location
    {Sept. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Doing Software Development “Inspection Check application using ASP.NET and VB.NET”.}
        \item {Doing Maintenance \& Preventive on Filling Machine.}
        \item {Doing Maintenance \& Preventive Process Machine SKID.}
        \item {Knowledge Gained: VB.net, ASP.net, Desktop Application, Maintenance system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {PT Datareka Integrasia Teknologi}
    {Cimahi, West Java, Indonesia} % Location
    {March. 2017 - July. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Troubleshooting Board PCB of Security Panel}
        \item {Assembly Board PCB Controller and Power Supply using SMD Component}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Field Service Engineer} % Job title
    {Midea Electronics Indonesia} % Organization
    {North Jakarta, Indonesia} % Location
    {Jun. 2016 - August. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance and repair Air Conditioner.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
